% LaTeX resume using res.cls
\documentclass[margin]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{url}
\setlength{\textwidth}{5.3in} % set width of text portion
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  urlcolor=black
}

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Benjamin J. Siver}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip

 \address{1530 W. Superior St. \\ Chicago, IL 60642  \\ (847) 401-2257 }
 \address{\href{mailto:bsiver@gmail.com}{\nolinkurl{bsiver@gmail.com}}
  \\ \url{http://omega.cs.iit.edu/~bsiver}}

\begin{resume}

\section{OBJECTIVE}  Seeking a full-time position as a Software Developer. I will become a valuable team member by
utilizing my knowledge of computer science combined with excellent communication skills, past experience, and desire to learn.

\section{EXPERIENCE}

                {\sl Software Engineer} \hfill April 2015 - Present \\
                Curiosity.com, Chicago, IL
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Implemented the backend for a content following and notification system in Clojure.
                 \item Assisted with development of a major update to the company's Android app.
                 \item Improved internal development processes by introducing continuous integration and code quality monitoring.
                 \item Worked effectively at every level of the software stack, moving between teams as necessary.
                \end{itemize}

                {\sl Software Engineer III} \hfill June 2012 - April 2015 \\
                CME Group, Match Engine Development, Chicago, IL
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Responsible for full-stack development of an internal market surveillance web application, improving user experience, and optimizing code.
                 \item Contributed to both front end and back end facing components, with heavy usage of Java, Spring, OSGi, jQuery, JavaScript, and Backbone.js.
                 \item Helped eliminate redundant/legacy code using static code analysis, reducing technical debt by over \$15,000.
                 \item Conducted technical interviews to help identify new talented team members.
                 \item Effectively communicated with others in an agile environment, participated in daily Scrum meetings, sprint planning, and development retrospectives.
                \end{itemize}

                {\sl Android/Web Development Intern} \hfill            Summer 2011 \\
                CME Group, Enterprise Architecture Department, Chicago, IL
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Developed an Android application that displays market data in real time.
                 \item Created a RESTful web service using the Jersey implementation of JAX-RS.
                 \item Setup and configured a server running MongoDB and Apache/Tomcat
                 \end{itemize}

                {\sl Undergraduate Studies in Earthquake Information Technology Intern} \hfill        Summer 2010 \\
                University of Southern California, Los Angeles, CA
                 \begin{itemize} \itemsep -2pt
                  \item Collaborated with a small development team to extend an existing software project used for visualizing seismic data in 3D space.
                  \end{itemize}

\section{RELEVANT \\ SKILLS} {\sl Languages \& Libraries:} Java, Clojure, JavaScript, jQuery, Backbone.js, SQL, C \\
                				{\sl Frameworks \& Tools:} Spring, OSGi, Android, iOS, MongoDB, Git, Apache, Tomcat, Maven \\
                                {\sl Operating Systems:} Windows, Unix, OS X \\
                                {\sl Other:} Agile development, TDD, JIRA, Bamboo, Sonar, Code review, Pair programming

\section{EDUCATION} {\sl Bachelor of Science,} Computer Science \\
                % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		            %	Computer Modern (default) font
                Illinois Institute of Technology, Chicago, IL,
                2012 \\
                Heald Scholar \\


\end{resume}
\end{document}
